% Created 2018-05-08 Tue 14:28
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{natbib}
\usepackage[margin=1.3in]{geometry}
\input{/Users/jun/Dropbox/settings/my_macros.tex}
\date{Due date: May 15, 2018 at class}
\title{Exercise 1}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.1.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
\begin{enumerate}
\item The table below is the summary of age and height of a sandlot team. 
\begin{center}
\begin{tabular}[t]{ccccccccccc}
Number  & 1   & 2   & 3   & 4   & 5   & 6   & 7   & 8   & 9   & 10   \\ \hline 
Height (X) & 155 & 165 & 160 & 170 & 150 & 160 & 165 & 170 & 165 & 155  \\
Age (Y) & 13  & 15  & 14  & 15  & 12  & 13  & 14  & 15  & 15  & 12 
\end{tabular}
\end{center}
\begin{enumerate}
\item Find the mean, variance, and standard deviation of $X$.
\item What is the correlation between height and age? Is it positive or negative?
\item On average how much does height increase par age?
\end{enumerate}

\item As noted, the correlation coefficient ranges $[-1,1]$. For a variable $X$, find a variable $Y$ that makes $\corr(X,Y)$ equal to (a) 1; (b) 0; and (c) -1.

\item A car factory has two production lines A and B, where line A produces 60\% and B 40\% of the total products. The rejection rate of A is 10\%, while that of B is 20\%. Calculate the overall rejection rate of this factory (use the law of total probability).

\item Answer the following questions based on figure 1 and 2
\begin{enumerate}
\item Is the probability of getting 7 or more heads out of 10 tosses of a coin the same as the probability of getting 70 or more heads by tossing the same coin 100 times? If not, which is bigger?
\item Let $X$ be the number of heads in 10 tosses of a fair coin. Express the probability of the event of ``getting less than 2 or more than 8 heads'' in the form of $P(\cdots)$. Based on Fig.1, decide whether this probability is bigger than 0.1.
\end{enumerate}
\end{enumerate}
% Emacs 25.1.1 (Org mode 8.2.10)
\end{document}