% Created 2018-05-14 Mon 14:24
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{natbib}
\usepackage[margin=1.3in]{geometry}
\input{/Users/jun/Dropbox/settings/my_macros.tex}
\date{Due date: May 22, 2018 at class}
\title{Exercise 2}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.1.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
\begin{enumerate}
\item Consider drawing a ball from an urn. There are two urns A and B, where A contains 1 red out of 10 balls, whereas B has 5 out of 10. You don't know from which you are drawing. Now, 
\begin{enumerate}
\item You draw a ball from the urn and it was not red. Calculate the probability that the urn from which urn you drew was A. (ANSWER: This is the example in p.1)
\item Then you put back the ball and made a second try, and that was non-red again. Update the probability of the above hypothesis.
\end{enumerate}

\item ``The common symptom of this year's flu (H) is severe headache and dizziness (E). Suspect a flu if you have these symptoms.'' 
\begin{enumerate}
\item Find the posterior probability of flu when $P(H)=0.1, P(E|H)=0.8, P(E)=0.2$.
\item Find the posterior probability of flu when $P(H)=0.1, P(E|H)=0.8, P(E|\neg H)=0.1$.
\end{enumerate}

\item There are three boxes, A, B, C, only one of which contains a prize. Suppose you chose A. Then the bookmaker opens C, to show that it is empty. Now he asks: ``you can change your mind and select B, if you like. Do you?'' Should you switch, or stick to your original choice? Justify your answer.
\end{enumerate}
% Emacs 25.1.1 (Org mode 8.2.10)
\end{document}